The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-03-24 manuscript/manuscript.tex
update the paper with corrected AB LR and "Vege-derived" Mstar.

The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. We compare the \mbh-\lhost~and \mbh-\smass~relations to those of local active galaxies, accounting for selection effects, to infer their evolution. The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that the BHs at higher redshift resides in less luminous galaxies than today. The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations. Considering that our sample are composed of bulge and disk components, we are forced to concluded that our results consistent to a scenario that the growth of the black hole predates that of the bulge.
\end{abstract}

@@

Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed bulge luminosity compared to the local relations. This offset is consistent with a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.

In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007, Lauer2007}. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.

In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest \citep{DeG++15}. In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).

@@

We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$. The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, a near-infrared (0.9-1.8 $\mu m$) spectrograph have with 400 apertures. The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}. Overall, our final sample is composed of 32 new observations by HST/WFC3. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

@@

\subsection{Comparison sample}
\textcolor{blue}{
We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For calibrating with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point. The sample by B10 consistent 19 \mbh-\lhost\ relations with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contains 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to the higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}. It is worth note that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, it is the local \mbh-\smass$_{Bulge}$ relation that we compared. }

\textcolor{blue}{
Including the compared samples at the intermediate redshift range would help to understand the redshift evolution of these correlations. We compared intermediate redshift AGNs for the \mbh-\lhost\ relation include 52 sample by \citet{Park15} at $0.36<z<0.57$ and 27 sample by \citet{Bennert11, SS13} at $0.5<z<1.9$. Moreover, \citet{SS13} also derive the \smass\ which enable us to compare to the \mbh-\smass\ relation at $0.5<z<1.2$. }

\subsection{BH masses}
\label{mbh}
 %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references. Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent. Thus, we adopt the virial formalism from \citet{Schulze2018}:

@@

Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. 14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value. We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.

\section{\hst\ observations}
\label{observation}
%\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line ($4000\AA$) is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

%Drizzling, background noise...
For each of the 32 new AGNs we took six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). Table~\ref{tab:objlist} lists the details of the observation. The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel. 
To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.

Multi-band information provides the spectral energy distributions (SED) at a more precise level. 21/32 of our sample have rest-frame UV images by \citet{Scoville2007}. Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).

@@

%\section{Analysis}
\subsection{PSF library}
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be vary across the detector and with time, due to the effect of aberrations and breathing. Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}. Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program. The selection consists of the following steps. We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}. A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates. We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects. In the end, the PSF library contains 78 and 37 PSFs for F140W and F125W, respectively.

@@

\subsection{Host galaxy properties}
We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude. 18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit the overall sample. We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples. Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample. Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty level raised by this K-correction is within 0.05~mag. We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.

Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted. The raised uncertainty level to the stellar mass is expected to be within 0.1~dex.

@@

\subsection{\mbh-\smass\ relation}
Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution. In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the mass distributions for the three samples are very similar. Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$. We obtain the $\gamma  = 0.49 \pm 0.19$ which slightly indicates as the positive, see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b). We highlight that our results are less biased in both the measurement of \mbh\ and \smass.

@@

We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value. We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.

@@

\section*{Acknowledgments}
Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. These observations are associated with programs
\#15115.

@@

SB, TT and AJS acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.

@@

CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.15\\-0.11}$ &$10.85\substack{+0.18\\-0.15}$\\[3pt]
CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.15\\-0.11}$ &$10.21\substack{+0.18\\-0.15}$\\[3pt]
CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.52\\-0.23}$ &$10.66\substack{+0.53\\-0.25}$\\[3pt]
CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.03\\-0.03}$ &$10.85\substack{+0.10\\-0.10}$\\[3pt]
CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.11\\-0.09}$ &$10.98\substack{+0.14\\-0.13}$\\[3pt]
CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.15\\-0.11}$ &$10.89\substack{+0.18\\-0.15}$\\[3pt]
CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.14\\-0.11}$ &$10.97\substack{+0.17\\-0.15}$\\[3pt]

>>>>

The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. We compare the \mbh-\lhost~and \mbh-\smass~relations to those of local active galaxies, accounting for selection effects, to infer their evolution. The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that at fixed mass BHs 8-10Gyrs ago reside in less luminous galaxies than today. Furthermore, the \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations. Considering that our sample are composed of bulge and disk components, the evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.
\end{abstract}

@@

Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations. It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.

In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007, Lauer2007}. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.

In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest \citep{DeG++15}. In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality of our data, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex) [what does this mean?].

@@

We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$. The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, covering the wavelength range 0.9-1.8 $\mu m$. The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}. Overall, our final sample is composed of 32 new observations by HST/WFC3. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

@@

\subsection{Comparison sample}
\textcolor{blue}{
We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point. The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to the higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}. It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities. }

\textcolor{blue}{
We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations. We select samples that were analyzed by members of our team, in order to ensure uniform measurements. The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$. Moreover, \citet{SS13} also derive the \smass\ which enable us to compare to the \mbh-\smass\ relation at $0.5<z<1.2$. }

\subsection{BH masses}
\label{mbh}
 %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator is very consistent ($<0.03$~dex r.m.s. or mean?) between the two references. Moreover, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ is consistent. Thus, we adopt the virial formalism from \citet{Schulze2018}:

@@

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. 14 of the systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value. We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.

\section{\hst\ observations}
\label{observation}
%\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\

High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. For this purpose, all the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as part of the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

%Drizzling, background noise...
For each of the 32 new AGNs we obtained six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). Table~\ref{tab:objlist} lists the details of the observation. The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel. 
To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool.

Multi-band information provides the spectral energy distributions (SED) at a more precise level. 21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}. Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).

@@

%\section{Analysis}
\subsection{PSF library}
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the point source is bright relative to the host. The PSF is known to be vary across the detector and with time, due to the effects of aberrations and breathing. Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}. Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program. The selection consists of the following steps. We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}. A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates. We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects. In the end, the PSF library contains 78 and 37 PSFs imaged through filters F140W and F125W, respectively.

@@

\subsection{Host galaxy properties}
We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude. 18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample. We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples. Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample. Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag. We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.

Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted. The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).

@@

\subsection{\mbh-\smass\ relation}
Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution. In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the mass distributions for the three samples are very similar. Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$. We obtain the $\gamma  = 0.49 \pm 0.19$, i.e. tentative evidence for evolution , see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b). We highlight that our results are less biased in both the measurement of \mbh\ and \smass.

@@

We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value. We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively. We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.

@@

\section*{Acknowledgments}
Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. These observations are associated with programs
\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555

@@

XD and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.

@@

CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$\\[3pt]
CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$\\[3pt]
CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$\\[3pt]
CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$\\[3pt]
CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$\\[3pt]
CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$\\[3pt]
CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$\\[3pt]
CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$\\[3pt]
